---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Assignment2

<!-- badges: start -->
<!-- badges: end -->

The goal of Assignment2 is to learn wrapping functions inside an R package. The package contains a subsidy function that calculates the amount of subsidy received in teh form of reimbursment, based on base value and subsidy percentage. 

## Installation

You can install the released version of Assignment2 from [CRAN](https://CRAN.R-project.org) with:

``` r
devtools::install_github("berudri/Assignment2)
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Assignment2)
subsidy(1300,40)
```

You can also use the other two functions that specify the amount of subsidy"
```{r}
fifty(2450)
eighty(2450)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.


Don't forget to commit and push the resulting figure files, so they display on GitHub!
